### 2017-04-19 Paper Drafts/Draft 0/Draft0.tex
Spectrogram figure and Data Description

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Review Volume (last updated on 20-4-2015)                            %%
%% Trim Size: 9in x 6in                                                 %%
%% Text Area: 7.35in (include runningheads) x 4.5in                     %%
%% Main Text: 10 on 13pt                                                %%
%% For support: Yolande Koh, <ykoh@wspc.com.sg>                         %%
%%              D. Rajesh Babu, <rajesh@wspc.com.sg>                    %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%\documentclass[wsdraft]{ws-rv9x6} % to draw border line around text area
\documentclass{ws-rv9x6}
\usepackage{subfigure}   % required only when side-by-side / subfigures are used
\usepackage{ws-rv-thm}   % comment this line when `amsthm / theorem / ntheorem` package is used
\usepackage{ws-rv-van}   % numbered citation & references (default)
%\usepackage{ws-index}   % to produce multiple indexes
\makeindex
%\newindex{aindx}{adx}{and}{Author Index}       % author index
%\renewindex{default}{idx}{ind}{Subject Index}  % subject index

@@

%\tableofcontents

\section{Introduction}

@@

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Review Volume (last updated on 20-4-2015)                            %%
%% Trim Size: 9in x 6in                                                 %%
%% Text Area: 7.35in (include runningheads) x 4.5in                     %%
%% Main Text: 10 on 13pt                                                %%
%% For support: Yolande Koh, <ykoh@wspc.com.sg>                         %%
%%              D. Rajesh Babu, <rajesh@wspc.com.sg>                    %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
\documentclass[wsdraft]{ws-rv9x6} % to draw border line around text area
%\documentclass{ws-rv9x6}
\usepackage{subfigure}   % required only when side-by-side / subfigures are used
\usepackage{ws-rv-thm}   % comment this line when `amsthm / theorem / ntheorem` package is used
\usepackage{ws-rv-van}   % numbered citation & references (default)
%\usepackage{ws-index}   % to produce multiple indexes
\makeindex
%\newindex{aindx}{adx}{and}{Author Index}       % author index
%\renewindex{default}{idx}{ind}{Subject Index}  % subject index

@@

%\tableofcontents
\section{Introduction}

@@

\begin{figure}[ht]
	\centerline{
		\subfigure[Broadband sweep, multiharmonic - \textit{Antrozous pallidus}]
		{\includegraphics[width=1.5in]{../Figures/anpaSpectrogram.eps}\label{fig::anpa}}
		\hspace*{4pt}
		\subfigure[Narrowband, multiharmonic - \textit{Balantiopteryx plicata
			}]
		{\includegraphics[width=1.5in]{../Figures/baplSpectrogram.eps}\label{fig::bapl}}
	}
	\centerline{
		\subfigure[Broadband sweep, single harmonic - \textit{Myotis yumanensis}]
		{\includegraphics[width=1.5in]{../Figures/myyuSpectrogram.eps}\label{fig::myyu}}
		\hspace*{4pt}
		\subfigure[Constant frequency with broadband sweep - \textit{Pteronotus parnellii}]
		{\includegraphics[width=1.5in]{../Figures/ptpaSpectrogram.eps}\label{fig::ptpa}}
	}
	\caption{Representative call spectrograms for some bat species, demonstrating echolocation call structures.}\label{fig::spectrogram}
\end{figure}

@@

\subsection{Data Description}

The post processed echolocation call data accompanying Stathopoulos et al. \cite{stathopoulos2017bat} was used in this analysis. Echolocation calls were recorded across north and central Mexico with a Pettersson 1000x bat detector (Pettersson Elektronik AB, Uppsala, Sweden). Live trapped bats were measured and identified to species level using field keys.\cite{ceballos2005mamiferos} \cite{medellin2sanchez} Bats were recorded either while released from the hand or while tied to a zip line. The bat detector was set to record calls manually in real time, full spectrum at 500 kHz. 
In total the dataset consists of 22 species in five families, 449 individual bats and 1814 individual echolocation call recordings.

\begin{table}[ht]
	\tbl{Echolocation Call Dataset Statistics}
	{\begin{tabular}{@{}lcc@{}} \toprule
			Species & Individuals & Calls \\ \colrule
			Family: Emballonuridae & & \\
			1 \textit{Balantiopteryx plicata} & 16 & 100 \\
			\\
			Family: Molossidae && \\
			2 \textit{Nyctinomops femorosaccus} & 16 & 100 \\
			3 \textit{Tadarida brasiliensis} & 49 & 100  \\
			\\
			Family: Vespertilionidae && \\
			4 \textit{Antrozous pallidus} & 58 & 100 \\
			5 \textit{Eptesicus fuscus} & 74 & 100 \\
			6 \textit{Idionycteris phyllotis} & 6 & 100 \\
			7 \textit{Lasiurus blossevillii} & 10 & 90 \\
			8 \textit{Lasiurus cinereus} & 5 & 42 \\
			9 \textit{Lasiurus xanthinus} & 8 & 100 \\
			10 \textit{Myotis volans} & 8 & 100 \\
			11 \textit{Myotis yumanensis} & 5 & 89 \\
			12 \textit{Pipistrellus hesperus} & 85 & 100 \\
			\\
			Family: Mormoopidae && \\
			13 \textit{Mormoops megalophylla} & 10 & 100 \\
			14 \textit{Pteronotus davyi} & 8 & 100 \\
			15 \textit{Pteronotus parnellii} & 23 & 100 \\
			16 \textit{Pteronotus personatus} & 7 & 51 \\
			\\
			Family:Phyllostomidae && \\
			17 \textit{Artibeus jamaicensis} & 11 & 82 \\
			18 \textit{Desmodus rotundus} & 6 & 38 \\
			19 \textit{Leptonycteris yerbabuenae} & 26 & 100 \\
			20 \textit{Macrotus californicus} & 6 & 53 \\
			21 \textit{Sturnira ludovici} & 8 & 51 \\
			22 \textit{Sturnira lilium} & 4 & 20 \\
			\botrule
		\end{tabular}
	}
	\begin{tabnote}
		$^{\text a}$Sample table footnote.
	\end{tabnote}
	\label{tab::dataset}
\end{table}

The 
The echolocation call dataset used for this study is the
